%-------------------------------------
% LaTeX Resume for Software Engineers
% Author : Leslie Cheng
% License : MIT
%-------------------------------------

\documentclass[12pt]{article}
\usepackage[letterpaper]{geometry}

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage{ifxetex}
\ifxetex
  \usepackage{fontspec}
  \usepackage[xetex]{hyperref}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[pdftex]{hyperref}
\fi
\usepackage{fontawesome}
\usepackage[sfdefault,light]{FiraSans}
\usepackage{anyfontsize}
\usepackage{xcolor}
\usepackage{tabularx}

\def \fullname {Rich Churcher}
\def \subtitle {Senior Platform / SRE}

\def \linkedinicon {\faLinkedin}
\def \linkedinlink {https://linkedin.com/in/dwight-schrute/}
\def \linkedintext {/richchurcher}

\def \phoneicon {\faPhone}
\def \phonetext {+64-21-126-3919}

\def \emailicon {\faEnvelope}
\def \emaillink {mailto:rich.churcher@gmail.com}
\def \emailtext {rich.churcher@gmail.com}

\def \githubicon {\faGithub}
\def \githublink {https://github.com/bas-ie}
\def \githubtext {/bas-ie}

% \def \websiteicon {\faGlobe}
% \def \websitelink {https://google.com/}
% \def \websitetext {richchurcher.me}

\def \headertype {\doublecol} % \singlecol or \doublecol

\def \entryspacing {0em}

\def \bulletstyle {\faAngleRight}

\definecolor{primary}{HTML}{1a1a1a}
\definecolor{secondary}{HTML}{2d6a4f}
\definecolor{accent}{HTML}{52606d}
\definecolor{muted}{HTML}{8a94a0}
\definecolor{links}{HTML}{2d6a4f}

\def \linkedin {\linkedinicon \hspace{1em}\href{\linkedinlink}{\linkedintext}}
\def \phone {\phoneicon \hspace{1em}{\phonetext}}
\def \email {\emailicon \hspace{1em}\href{\emaillink}{\emailtext}}
\def \github {\githubicon \hspace{1em}\href{\githublink}{\githubtext}}
% \def \website {\websiteicon \hspace{1em}\href{\websitelink}{\websitetext}}

% margins
\addtolength{\oddsidemargin}{-14mm}
\addtolength{\evensidemargin}{-14mm}
\addtolength{\textwidth}{28mm}
\addtolength{\topmargin}{-16mm}
\addtolength{\textheight}{28mm}

\hypersetup{
    colorlinks=true,
    urlcolor=links,
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0mm}

% sections
\renewcommand{\section}[2]{\vspace{1.2ex}
  {\color{secondary}\normalsize#1\hspace{0.8em}\textbf{\MakeUppercase{#2}}}\par\vspace{-0.6ex}
  {\color{secondary}\rule{\textwidth}{0.4pt}}\vspace{-0.8ex}
}

% entry start and end, for spacing
\newcommand{\resumeEntryStart}{\begin{itemize}[leftmargin=2.5mm]}
\newcommand{\resumeEntryEnd}{\end{itemize}\vspace{\entryspacing}}

% lists
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=4.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Resume item
\renewcommand{\labelitemii}{\bulletstyle}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-0.9ex}}
  }
}

% entry with title, subheading, date(s), and location
\newcommand{\resumeEntryTSDL}[4]{
  \vspace{-0.5ex}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{5em}}r}
      \textbf{\color{primary}#1} & {\firabook\color{muted}\small#2} \\
      \textit{\color{accent}\small#3} & \textit{\color{muted}\small#4} \\
    \end{tabularx}\vspace{-0.9ex}
}

% entry with title and date(s)
\newcommand{\resumeEntryTD}[2]{
  \vspace{-0.5ex}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{5em}}r}
      \textbf{\color{primary}#1} & {\firabook\color{muted}\small#2} \\
    \end{tabularx}\vspace{-0.9ex}
}

% double column header
\newcommand{\doublecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[c]{l}
        \fontsize{28}{34}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
          {\textit{\subtitle}}
      \end{tabular}\vspace{0.8ex}
    } & {
      \begin{tabular}[c]{l@{\hspace{1em}}l}
        {\small#4} & {\small#1} \\
        {\small#5} & {\small#2} \\
        {\small#6} & {\small#3}
      \end{tabular}
    }
  \end{tabularx}
}

% single column header
\newcommand{\singlecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[b]{l}
        \fontsize{28}{34}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l}
        {\small#1} \\
        {\small#2} \\
        {\small#3} \\
        {\small#4} \\
        {\small#5} \\
        {\small#6}
      \end{tabular}
    }
  \end{tabularx}
}

\begin{document}

% \headertype{\linkedin}{\github}{\website}{\phone}{\email}{}
\headertype{\linkedin}{\github}{}{\phone}{\email}{}

\section{\faUser}{Profile}

  \small Senior platform and site reliability engineer with 8+ years shipping and operating production systems on Linux and AWS.
  \par\vspace{0.4ex}
  Second career after 14 years as a paediatric intensive care nurse, including flight transport --- I bring clinical incident-response discipline to production operations: calm under load, bias to root cause, triage what matters first.
  \par\vspace{0.4ex}
  Self-taught, remote-first, and happiest in small teams where autonomy and pragmatism matter more than process.

\section{\faWrench}{Skills}

  \begin{tabularx}{\textwidth}{@{}l@{\hspace{1.5em}}X@{}}
    \textbf{Cloud / Infra} & AWS (EC2, ECS, EKS, Lambda, RDS, DynamoDB, Kinesis, IoT Core, EventBridge), Terraform, Spacelift, Kubernetes. \\
    \textbf{Languages}     & Go, Python, TypeScript, Rust, Bash, sundry others. \\
    \textbf{Platform / CI} & GitHub Actions, CircleCI, Concourse, Docker, Linux (Arch, Amazon, various other flavours), Postgres, MySQL. \\
    \textbf{Observability} & Datadog, Grafana, CloudWatch, New Relic, Sentry; incident management and on-call design. \\
    \textbf{Data}          & Athena, Redshift, Mage, ETL pipeline migration. \\
    \textbf{AI workflow}   & Claude Code in daily workflow; CodeRabbit and Copilot integrated into PR review pipelines; agent-assisted migration and code archaeology. \\
    \textbf{AI infrastructure} & Local inference via ollama (Qwen3-Coder). MCP servers to GitHub, AWS. Developer tooling for ops workflows. \\
  \end{tabularx}

\section{\faPieChart}{Experience}

  \resumeEntryStart
    \resumeEntryTSDL
      {Multitudes}{Nov 2025 - Mar 2026 (Contract)}
      {Software Engineer}{Remote}
    \resumeItemListStart
      \resumeItem {Implemented Okta/Auth0 enterprise SSO.}
      \resumeItem {Updating and migrating data ingestion and processing workflows using Mage and Athena.}
      \resumeItem {Claude Code daily driver for exploration, diagnostic helper, documentation automation, compressing ramp-up on an unfamiliar codebase within a short contract window.}
    \resumeItemListEnd
  \resumeEntryEnd
  
  \resumeEntryStart
    \resumeEntryTSDL
      {Basis}{Oct 2024 -- November 2025}
      {Site Reliability Engineer}{Remote}
    \resumeItemListStart
      \resumeItem {Created an incident management plan for a complex production environment that included IoT, mobile, and cloud services components.}
      \resumeItem {Migrated an ECS-based datalake stack to Kubernetes.}
      \resumeItem {Migrated the terraform-based IaC environment from Terraform Cloud to Spacelift.}
      \resumeItem {Claude Code in daily workflow, Copilot integrated into PR review pipelines to raise baseline review quality and catch regressions earlier.}
    \resumeItemListEnd
  \resumeEntryEnd
  
  \resumeEntryStart
    \resumeEntryTSDL
      {Lightspeed Commerce}{Oct 2023 -- Oct 2024}
      {Senior Platform Engineer}{Remote}
    \resumeItemListStart
      \resumeItem {Wrote automated tooling in Go to traverse hundreds of GitHub repositories to update versions and configuration values.}
      \resumeItem {Implemented a custom GitHub runner to launch ops tasks in the production environment (database maintenance, new Kafka topics), reducing maintenance time and unblocking developer workflows.}
    \resumeItemListEnd
  \resumeEntryEnd
  
  \resumeEntryStart
    \resumeEntryTSDL
      {Cogo}{Dec 2022 -- Oct 2023}
      {Senior Platform Engineer}{Remote}
    \resumeItemListStart
      \resumeItem {Reduced development environment costs by more than half in some cases using Terraform to conduct timed teardowns via GitHub Actions.}
      \resumeItem {Increased the observability of costs across AWS accounts using Python and the AWS API.}
      \resumeItem {Negotiated, planned, and rewrote on-call and incident management documentation, making the on-call engineering experience safer and more predictable.}
      \resumeItem {Troubleshoot CI, deployment and runtime issues in a containerised Elixir (Phoenix) environment.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {Spidertracks}{Apr 2021 -- Dec 2022}
      {Senior Software Engineer}{Remote}
    \resumeItemListStart
      \resumeItem {Mapped network ingress from Iridium satellites and cellular devices through legacy infrastructure to mitigate Java server load issues.}
      \resumeItem {Rebuilt on-call team and ops culture from the ground up after company was acquired.}
      \resumeItem {Centralised scattered observability across New Relic, Grafana, CloudWatch, Sumologic, and Sentry, laying groundwork for a single-pane-of-glass migration.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {Eventfinda}{Nov 2020 -- Apr 2021}
      {Senior Software Engineer (Contract)}{Remote}
    \resumeItemListStart
        \resumeItem {Assisted with and advised on upgrading a large existing codebase (React, PHP).}
        \resumeItem {Improved test coverage of legacy code in order to avoid regressions when migrating to newer systems.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {BuildSpider}{Sep 2019 -- Nov 2020}
      {Senior Software Engineer (Contract)}{Remote}
    \resumeItemListStart
      \resumeItem {Wrote extensive Postgres functions and migrations as part of a GraphQL API using Postgraphile.}
      \resumeItem {Added a secure S3-backed file library feature using React, Relay, and role-based permissions using Postgres row-level security.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {HYPR Innovation}{Feb 2019 -- Sep 2019}
      {Senior Software Engineer (Contract)}{Remote}
    \resumeItemListStart
      \resumeItem {React/MobX frontend and Node/Kafka microservices processing animal data for a large agricorporation.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {Hylo}{Mar 2017 -- Aug 2018}
      {Software Engineer (Contract)}{Remote (San Francisco)}
    \resumeItemListStart
      \resumeItem {React Native mobile app for a distributed SF-based team; performance and deep-linking work.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTD
      {Earlier contract and teaching roles (2015 -- 2018):}{2015 -- 2018}
    \resumeItemListStart
      \resumeItem {Enspiral Dev Academy, Saatchi \& Saatchi, BKA Digital Outfitters --- React, Node, curriculum design.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {Paediatric Intensive Care Nurse}{1999 -- 2015}
      {Starship Hospital (Auckland) \& Children's Hospital at Westmead (Sydney).}{}
    \resumeItemListStart
      \resumeItem {PICU flight transport team, ECMO team.}
    \resumeItemListEnd
  \resumeEntryEnd

\section{\faFlask}{Projects}

  \resumeEntryStart
    \resumeEntryTSDL
      {Bucket}{Apr 2022 -- Jan 2025}
      {Senior Software Engineer (Volunteer)}{Remote}
    \resumeItemListStart
      \resumeItem {Sole developer and platform engineer for Fairground Foundation, working on Bucket, an environment crowdfunding application.}
      \resumeItem {Go, Flutter, Figma, Terraform, AWS. Low-cost strategies for a pre-launch product.}
    \resumeItemListEnd
  \resumeEntryEnd

\section{\faGraduationCap}{Education}

  \resumeEntryStart
    \resumeEntryTSDL
      {Otago Polytechnic}{1996 -- 1998}
      {Bachelor of Nursing}{Dunedin}
  \resumeEntryEnd

\end{document}
